Real Estate

### 2022-11-02 src/real_estate.Rmd
calculated separate real estate scores for median rent and avg rent

```{r}
# weights from owen
real_estate_weights <- c(0.35, 0.20, 0.15, 0.10, 0.10, 0.10, 0.10)

#make real_estate_score column
n_MSA_realEstate <- n_MSA_realEstate %>% 
  select(cbsa, msa, starts_with("n_")) %>% 
  mutate(real_estate_score = msa) #this is just a place holder
```

@@

weighted_RE_data <- n_MSA_realEstate %>% 
  mutate(weighted_pop_change = 0.3 * n_pop_change) %>% 
  mutate(weight_emp = 0.25 * n_employ_change)

for (i in size[1]) {
  MSA_x_data <- c(n_MSA_realEstate$n_pop_change[i],
                  n_MSA_realEstate$n_employ_change[i],
                  n_MSA_realEstate$n_avg_occupancy[i],
                  n_MSA_realEstate$n_rent_change[i],
                  n_MSA_realEstate$n_med_rent_to_income_inverted[i],
                  n_MSA_realEstate$n_avg_rent_to_income_inverted[i], # compare avg rent and median rent
                  n_MSA_realEstate$n_income_to_homeprice[i]
                  )
  n_MSA_realEstate$real_estate_score[i] = weighted.mean(MSA_x_data, real_estate_weights)
}

@@

>>>>

```{r}
# manually check weighted score
n_MSA_realEstate<- n_MSA_realEstate %>% 
  mutate(weighted_pop_change = 0.35 * n_pop_change) %>% 
  mutate(weight_emp = 0.20 * n_employ_change) %>% 
  mutate(weighted_occ = 0.15 * n_avg_occupancy) %>% 
  mutate(weighted_rent_change = 0.10 * n_rent_change) %>% 
  mutate(weighted_med_rent_income = 0.10 * n_med_rent_to_income_inverted) %>% 
  mutate(weight_income_homeprice = 0.10 * n_income_to_homeprice) %>% 
  mutate(total_score = weighted_pop_change + weight_emp + weighted_occ + weighted_rent_change + weighted_med_rent_income + weight_income_homeprice)
```

```{r}
# weights from owen
real_estate_weights <- c(0.35, 0.20, 0.15, 0.10, 0.10, 0.10)

#make real_estate_score column
n_MSA_realEstate <- n_MSA_realEstate %>% 
  select(cbsa, msa, starts_with("n_"), total_score) %>% 
  mutate(real_estate_score = msa) %>% #this is just a place holder
  mutate(RE_score_avg_rent = msa)
```

@@

for (i in 1:size[1]) {
  MSA_x_data <- c(n_MSA_realEstate$n_pop_change[i],
                  n_MSA_realEstate$n_employ_change[i],
                  n_MSA_realEstate$n_avg_occupancy[i],
                  n_MSA_realEstate$n_rent_change[i],
                  n_MSA_realEstate$n_med_rent_to_income_inverted[i], 
                  n_MSA_realEstate$n_income_to_homeprice[i]
                  )
  n_MSA_realEstate$real_estate_score[i] = weighted.mean(MSA_x_data, real_estate_weights)
}

@@

```{r}

# score using average rent
for (i in 1:size[1]) {
  MSA_x_data <- c(n_MSA_realEstate$n_pop_change[i],
                  n_MSA_realEstate$n_employ_change[i],
                  n_MSA_realEstate$n_avg_occupancy[i],
                  n_MSA_realEstate$n_rent_change[i],
                  n_MSA_realEstate$n_avg_rent_to_income_inverted[i], # compare avg rent and median rent
                  n_MSA_realEstate$n_income_to_homeprice[i]
                  )
  n_MSA_realEstate$RE_score_avg_rent[i] = weighted.mean(MSA_x_data, real_estate_weights)
}
```
